Hydra Battles and Cie

### 2021-08-28 doc/part-hydras.tex
improving the pdf (up to p. 35)

We chose to call \emph{standard} the kind of battles which appear  most often in the literature and correspond to an arithmetic progression of the replication factor : $0,1,2,3, \dots$

@@

\input{movies/snippets/Hydra_Lemmas/battleTrans}

@@

\begin{itemize}
\item At each round, Hercules chops off the rightmost head of the hydra.
\item The battle is called \emph{standard}\footnote{This appellation is ours. If there is a better one, we will change it.}: at the round number $i$, the expected replication is $i$.
\end{itemize}

@@

@@

For instance Fig~\vref{fig:hinit-plusn} shows the hydra (\texttt{hyd 3 4 2}). The hydra (\texttt{hyd 0 0 0})  is the ``final'' hydra of any terminating battle, {i.e.},
a tree whith exactly one node and no edge.

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[thick, scale=0.30]
 \node (foot) at (15,0) {$\bullet$};
\node (a) at  (3,4) {$\bullet$};
\node (b) at  (6,4) {$\bullet$};
\node (c) at  (9,4) {$\bullet$};
\node (d) at  (13,4) {$\bullet$};
\node (e) at  (16,4) {$\bullet$};
\node (f) at  (19,4) {$\bullet$};
\node (g) at  (22,4) {$\bullet$};
\node (h) at  (25,4) {$\Smiley[1][green]$};
\node (i) at  (28,4) {$\Smiley[1][green]$};
\node (aa) at  (2.5,8) {$\Smiley[1][green]$};
\node (ab) at  (3.5,8) {$\Smiley[1][green]$};
\node (ba) at  (5.5,8) {$\Smiley[1][green]$};
\node (bb) at  (6.5,8) {$\Smiley[1][green]$};
\node (ca) at  (8.5,8) {$\Smiley[1][green]$};
\node (cb) at  (9.5,8) {$\Smiley[1][green]$};
\node (da) at  (13,8) {$\Smiley[1][green]$};
\node (ea) at  (16,8) {$\Smiley[1][green]$};
\node (fa) at  (19,8) {$\Smiley[1][green]$};
\node (ga) at  (22,8) {$\Smiley[1][green]$};
\draw (foot) -- (a);
\draw (foot) -- (b);
\draw (foot) -- (c);
\draw (foot) -- (d);
\draw (foot) -- (e);
\draw (foot) -- (f);
\draw (foot) -- (g);
\draw (foot) -- (h);
\draw (foot) -- (i);
\draw (a) -- (aa);
\draw (a) -- (ab);
\draw (b) -- (ba);
\draw (b) -- (bb);
\draw (c) -- (ca);
\draw (c) -- (cb);
\draw (d) -- (da);
\draw (e) -- (ea);
\draw (f) -- (fa);
\draw (g) -- (ga);
% \node (a) at  (3,4) {$\bullet$};
% \node (h1) at  (1,6) 
% \node (h2) at  (3,6) {$\Smiley[1][green]$};
% \node (h3) at  (6,6) {$\Smiley[1][green]$};
% \node (h4) at  (6,6) {$\Smiley[1][green]$};
% \draw (foot) -- (n1);
% \draw (n1) to   [bend left=20] (h1);
% \draw (n1) to   (h2);
% \draw (n1) to   [bend right=20] (h3);
\end{tikzpicture}

>>>>

We chose to call \emph{standard}\footnote{This appellation is ours. If there is a better one, we will change it.} the kind of battles which appear  most often in the literature and correspond to an arithmetic progression of the replication factor : $0,1,2,3, \dots$

@@

\vspace{4pt}
\emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Lemmas.html}{Hydra.Hydra\_Lemmas}}

\noindent
\input{movies/snippets/Hydra_Lemmas/battleTrans}

@@

\begin{itemize}
\item At each round, Hercules chops off the rightmost head of the hydra.
\item The battle is {standard}: at the round number $i$, the expected replication is $i$.
\end{itemize}

@@

\emph{From Module~\href{../theories/html/hydras.Hydra.BigBattle.html}{Hydra.BigBattle}}

@@

For instance, the hydra shown in  Fig~\ref{fig:hinit-plusn} is  (\texttt{hyd 3 4 2}). The hydra (\texttt{hyd 0 0 0})  is the ``final'' hydra of any terminating battle, {i.e.},
a tree whith exactly one node and no edge.

\begin{figure}[h]
  \centering
  \begin{tikzpicture}[thick, scale=0.30]
 \node (foot) at (15,0) {$\bullet$};
\node (a) at  (3,4) {$\bullet$};
\node (b) at  (6,4) {$\bullet$};
\node (c) at  (9,4) {$\bullet$};
\node (d) at  (13,4) {$\bullet$};
\node (e) at  (16,4) {$\bullet$};
\node (f) at  (19,4) {$\bullet$};
\node (g) at  (22,4) {$\bullet$};
\node (h) at  (25,4) {$\Smiley[1][green]$};
\node (i) at  (28,4) {$\Smiley[1][green]$};
\node (aa) at  (2.5,8) {$\Smiley[1][green]$};
\node (ab) at  (3.5,8) {$\Smiley[1][green]$};
\node (ba) at  (5.5,8) {$\Smiley[1][green]$};
\node (bb) at  (6.5,8) {$\Smiley[1][green]$};
\node (ca) at  (8.5,8) {$\Smiley[1][green]$};
\node (cb) at  (9.5,8) {$\Smiley[1][green]$};
\node (da) at  (13,8) {$\Smiley[1][green]$};
\node (ea) at  (16,8) {$\Smiley[1][green]$};
\node (fa) at  (19,8) {$\Smiley[1][green]$};
\node (ga) at  (22,8) {$\Smiley[1][green]$};
\draw (foot) -- (a);
\draw (foot) -- (b);
\draw (foot) -- (c);
\draw (foot) -- (d);
\draw (foot) -- (e);
\draw (foot) -- (f);
\draw (foot) -- (g);
\draw (foot) -- (h);
\draw (foot) -- (i);
\draw (a) -- (aa);
\draw (a) -- (ab);
\draw (b) -- (ba);
\draw (b) -- (bb);
\draw (c) -- (ca);
\draw (c) -- (cb);
\draw (d) -- (da);
\draw (e) -- (ea);
\draw (f) -- (fa);
\draw (g) -- (ga);
\end{tikzpicture}
